\documentclass{article}


\usepackage{minted}
\usepackage{fancyhdr}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{caption}
\usepackage{listings}
\usepackage{physics}
\usepackage{mathtools}
\usepackage{xparse}
\usepackage{dsfont}
\usepackage{amsmath}
\usepackage{amssymb}


\title{	
	\normalfont\normalsize
	\textsc{University of Canterbury, School of Mathematics and Statistics}\\ % Your university, school and/or department name(s)
	\vspace{25pt} % Whitespace
	\rule{\linewidth}{0.5pt}\\ % Thin top horizontal rule
	\vspace{20pt} % Whitespace
	{\huge MATH240 Assignment 2 - Real Analysis}\\ % The assignment title
	\vspace{12pt} % Whitespace
	\rule{\linewidth}{2pt}\\ % Thick bottom horizontal rule
	\vspace{12pt} % Whitespace
}

\author{\LARGE Emma Hogan \\\\53837798} % Your name


\date{\normalsize\today} % Today's date (\today) or a custom date
\begin{document}
\begin{titlepage}
\maketitle
\end{titlepage}
\section*{Question 1}
\subsection*{Let S be a non-empty subset of the real numbers which is bounded above. Let c be a real number and define T = \{cx $\mid$ x $\in$ S\}. Show that, if c $>$ 0, then T is non empty, bounded above and that supT = csupS. Give an example of a set S as above, such that, with c = -1, the set T is still bounded above but supT $\ne$ csupS.}

\solution
To show \(T\) is non-empty, observe \(S\) \(\neq \emptyset\), so \(T = \{cx\) \(|\) \(x \in S\} \neq \emptyset\).
\\
\\
Since \(S\) is bounded above, by definition there exists some upper bound \(U\) such that \(x \leq U\) \(\forall\) \(x \in S\). So, by transitivity, \(cx \leq cU\) \(\forall\) \(x \in S\). Therefore, \(cU\) is an upper bound for \(T\).
\\
\\
Since \(S\) is non-empty and bounded above, we know \(supS\) exists. By definition of \(supS\), \(\forall\) \(s \in S\), \(s \leq supS\). So, since c is positive, \(cs \leq csupS\). This means that \(t \leq csupS\) \(\forall\) \(t \in t\) and therefore \(csupS\) is an upper bound for \(T\).
\\
\\
Since \(T\) is also non-empty and bounded above, we know \(supT\) also exists. Assume \(supT < csupS\). We will find a contradiction.
\\
\\
Since \(c > 0\):
\begin{align}
  \label{}
  supT < csupS \nonumber \\
  \Rightarrow \frac{supT}{c} < supS\nonumber
\end{align}
\\
By definition of \(supS\), for any value \(X < supS\), \(\exists\) \(s \in S\) such that \(s>X\). So, \(\exists\) \(s' \in S\) such that
\begin{align}
  \label{}
  s' > \frac{supT}{c} \nonumber \\
  \Rightarrow cs' > supT \nonumber
\end{align}
\\
\(cs' \in T\) by definition of \(T\), so \(cs' > supT\) is a contradiction.
\\
\begin{align}
  \label{}
  \therefore supT \geq csupS
\end{align}
\\
But \(csupS\) is an upper bound for \(T\).
\begin{align}
  \label{}
  \therefore supT \leq csupS
\end{align}
\\
And so from (1) and (2), we know:
\begin{align}
  \label{}
  supT = csupS \nonumber
\end{align}
\\
As an example of \(supT \neq supS\) when \(c=-1\), take \(S = \{-1,-2\}\), so \(supS = -1\). With \(c=-1\), \(T = \{1,2\}\) and \(supT = 2\). But \(csupS = 1 \neq 2\), so \(csupS \neq supT\).
\\
\\
This is true for any bounded \(S\) with \(|S| > 1\).
\\
\section*{Question 2}
\subsection*{(i) If \((x_n)\) is a sequence such that \(\lim|x_n| = 0\), prove that \(\lim x_n = 0\) also.}

\solution
\\
By definition of the limit, \(\lim|x_n| = 0 \Rightarrow \forall\) \(\mathcal{E} \geq 0\), \(\exists\) \(N \in \mathds{N}\) such that \(\forall\) \(n\) \(\geq N\),

\begin{align}
  \label{}
  ||x_n| - 0| \leq \mathcal{E} \nonumber \\
  \Rightarrow ||x_n|| \leq \mathcal{E} \nonumber \\
  \Rightarrow |x_n| \leq \mathcal{E} \nonumber \\
  \Rightarrow |x_n - 0| \leq \mathcal{E} \nonumber \\
  \Rightarrow \lim x_n = 0 \nonumber
\end{align}

\subsection*{(ii) Give an example of a sequence \((x_n)\) that does not converge but that \((|x_n|)\) converges.}
\solution
\\
Define \((x_n)\) by \(x_n\ = (-1)^n\) which does not converge.
\\
\\
\(|x_n| = |(-1)^n| = |-1|^n = 1\) so \((|x_n|)\) converges to 1.

\section*{Question 3}
\subsection*{Let $\sum x_n$ be a series that converges absolutely. Show that $\sum x^2_n$ converges.}
\solution
\\
\\
\\
Since \(\sum |x_n|\) converges, we know that $\lim_{n\to\infty} |x_n|$\(=0\). So, by definition of the limit, we know \(\exists\) \(N\) such that \(\forall\) \(n\) \(\geq N\), \(|x_n| \leq 1\).
\\
\\
We can remove a finite number of terms for the start of a series without change its behaviour. So, we consider \(\sum_{n=N}^{\infty} |x_n|\), so \(|x_n|\leq 1\) for every term in the sequence.
\\
\\
Note that since \(x_n^2 \geq 0\), \(|x_n|^2 = x_n^2 = |x_n^2|\). 
\\
\\
\(|x_n| \leq 1\) so \(|x_n|^2 = |x_n^2| \leq 1\).
\\
\\
\(|x_n^2| \leq |x_n| \forall n \geq N\), so, since \(\sum_{n=N}^{\infty} |x_n|\) is convergent, \(\sum_{n=N}^{\infty} |x_n^2|\) is also convergent. Once again, N is just a finite number so it does not change the behaviour of the series.
\\
\\
Therefore \(x_n^2\) is absolutely convergent, which implies it is convergent.
\section*{Question 4}
\subsection*{Write question 4 here}
\solution
\\
Solve question 4 here.
\section*{Question 5}
\subsection*{Write question 5 here}
\solution
\\
Solve question 5 here.
\end{center}
\end{document}
